---
title: "Many faces of Rmarkdown"
author:
- name: Selcan Aydin, Ph.D.
  url: https://selcan-aydin.netlify.app/
  affiliation: The Jackson Laboratory
  affiliation_url: https://www.jax.org/
date: "`r Sys.Date()`"
description: |
  Invited talk @ R-ladies Dammam
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Learn more about creating websites with Distill at:
# https://rstudio.github.io/distill/website.html

```

```{r meta, echo=FALSE}
library(metathis)
meta() %>%
  meta_general(
    description = "Introducing Rmarkdown",
    generator = "xaringan and remark.js"
  ) %>% 
  meta_name("github-repo" = "selcant/Rladies_Dammam_042021") %>% 
  meta_social(
    title = "Many faces of Rmarkdown",
    url = "",
    image = "https://repository-images.githubusercontent.com/288797104/d13f1700-e2cc-11ea-9ed7-0bf3a41af1e4",
    image_alt = "R Markdown hedgehog by Allison Horst",
    og_type = "website",
    twitter_card_type = "summary_large_image"
  )
```

## Welcome  

This website contains the materials for an invited talk for R-ladies Dammam by Dr. Selcan Aydin. 

You can download the .Rmd files needed for hands-on exercises here: <https://github.com/selcant/Rladies_Dammam_042021/blob/main/docs.zip>
<https://github.com/selcant/Rladies_Dammam_042021/blob/main/website_ex.zip>

```{r share-again, echo=FALSE}
xaringanExtra::use_share_again()
```

```{r embed-xaringan, echo=FALSE, fig.cap="[Slides](slides/index.html)", eval=FALSE}
xaringanExtra::embed_xaringan(url = "slides/index.html", ratio = "16:9")
```
\

## Prework

I assume that you have heard of [R Markdown](https://rmarkdown.rstudio.com/) and maybe gave knitting a try. If not, no worries you will get to try with us! This will be a very hands-on session where together we will:

+ Knit an Rmarkdown file to html. Make it prettier!

+ Build a website using Rmarkdown. Share it with the world?

Please make sure you have installed the packages below:

```{r eval=FALSE, echo=TRUE}
install.packages(c("tidyverse", "DT", "palmerpenguins"))
```

\

## Links

+ Link to this website: <https://many-faces.netlify.app/>

+ [Slides](slides/index.html)


## Acknowledgments {.appendix}

This website is made with the [distill package](https://rstudio.github.io/distill/) and a custom theme by Alison Hill & [Desirée De Leon](https://desiree.rbind.io/).

